Supplement History of Cheminformatics as part of Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-09 supplement_history.tex
more updates

\section{Historical Milestones}
The first chemical graphs were drawn by the Scottish chemist Willam
Cullen in 1758 \cite{bonchevrouvrey1991}, who initially called them
affinity graphs.  After developing the concept of bonds between atoms
(Couper, 1858) the first chemical graphs occured in publications of
Brown in 1864 and Cayley in 1874 \cite{bonchevrouvrey1991,brown2009}.

@@

>>>>

\section{Historical Milestones}
In this section we highlight the development of a variety of
cheminformatics concepts and techniques over time. The first chemical
graphs were drawn by the Scottish chemist Willam Cullen in 1758
\cite{bonchevrouvrey1991}, who initially called them affinity graphs.
After developing the concept of bonds between atoms (Couper, 1858) the
first chemical graphs occured in publications of Brown in 1864 and
Cayley in 1874 \cite{bonchevrouvrey1991,brown2009}.

@@

QSAR is one of the most well known applications of predictive
cheminformatics and originates with the work of Hansch
\cite{Hansch:1962vn} in 1962. While Hansch's approach focused on
property-activity relationships, true structure-activity relationships
originated with the work of Free and Wilson in 1964
\cite{Free:1964ys}. Subsequent work in this area led to 3D-QSAR
techniques including CoMFA \cite{Cramer:1988zr} and
CoMSIA\cite{Klebe:1994ly}.
